\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{array}
\usepackage{microtype}

\hypersetup{colorlinks=true,urlcolor=black,linkcolor=black}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}
\renewcommand{\arraystretch}{1.03}
\setlist[itemize]{leftmargin=1.15em, itemsep=1pt, topsep=1.5pt, parsep=0pt, partopsep=0pt}

\titleformat{\section}
  {\normalsize\bfseries\uppercase}
  {}
  {0pt}
  {}
  [\vspace{-2pt}\titlerule]
\titlespacing*{\section}{0pt}{7pt}{4pt}

\newcommand{\entry}[4]{%
  \begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X >{\raggedleft\arraybackslash}p{0.24\textwidth}@{}}
    {\small\textbf{#1}} & {\small #2} \\
    {\small\textit{#3}} & {\small\textit{#4}} \\
  \end{tabularx}\vspace{1.25pt}
}

\newcommand{\shortentry}[3]{%
  \begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X >{\raggedleft\arraybackslash}p{0.18\textwidth}@{}}
    {\small\textbf{#1}} & {\small #2} \\
    \multicolumn{2}{@{}>{\raggedright\arraybackslash}X@{}}{{\small\textit{#3}}} \\
  \end{tabularx}\vspace{1pt}
}

\newcommand{\publication}[5]{%
  \begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X@{}}
    {\small\bfseries\mbox{#1}} \\
    {\small #2 \quad | \quad #3} \\
    {\small #4} \\
    {\small \textit{#5}} \\
  \end{tabularx}\vspace{2pt}
}

\newcommand{\skillline}[2]{{\small\textbf{#1:} #2}\\[1pt]}

\begin{document}
\enlargethispage{3\baselineskip}

\begin{center}
    {\LARGE \textbf{Kexin Tan}}\\[3pt]
    Tokyo, Japan \;|\; (+81) 07074790623 \;|\; \href{mailto:bluellatan@gmail.com}{bluellatan@gmail.com} \;|\;
    \href{https://january-blue.github.io/}{january-blue.github.io} \;|\; \href{https://github.com/january-blue}{GitHub}
\end{center}
\vspace{-4pt}

\section*{Research Experience}

\entry
{Research Assistant Intern, NLP Lab, Fudan University}
{Shanghai, China}
{logic-and-NLP benchmarks; scholarly agentic systems}
{2025.10--Present}

\entry
{Teaching Assistant, Quantitative Risk Management, Fudan University}
{Shanghai, China}
{Supported Q\&A for international students}
{2020.07--2020.08}

\entry
{Research Assistant Intern, Green Finance Research Center, Fudan University}
{Shanghai, China}
{Literature translation \& collation for environmental economics research}
{2019.11--2020.02}

\section*{Selected Publications \& Preprints}
\vspace{-2pt}
{\small * denotes co-first authorship.}
\vspace{2pt}

\publication
{OpenNovelty: An LLM-Powered Agentic System for Verifiable Scholarly Novelty Assessment}
{arXiv preprint, 2026}
{M. Zhang*\textsuperscript{\dag}, \textbf{K. Tan}*, Y. Huang*, Y. Shen, C. Ma, L. Ju, X. Zhang, et al.}
{\href{https://arxiv.org/abs/2601.01576}{Paper} \;|\; \href{https://github.com/january-blue/OpenNovelty}{Code} \;|\; \href{https://opennovelty.org/}{Website}}
{Agentic scholarly assessment; evidence-grounded novelty analysis; peer-review assistance.}

\publication
{LLMEval-Fair: A Large-Scale Longitudinal Study on Robust and Fair Evaluation of Large Language Models}
{ACL Main, 2026}
{M. Zhang*\textsuperscript{\dag}, Y. Shen*, J. Deng*, Y. Wang*, H. Sha, \textbf{K. Tan}, Q. Peng, et al.}
{\href{https://arxiv.org/abs/2508.05452}{Paper} \;|\; \href{https://github.com/llmeval/LLMEval-Fair}{Code}}
{Dynamic LLM evaluation; contamination-resistant benchmarking; longitudinal model comparison.}

\publication
{Can Deep Research Agents Retrieve and Organize? Evaluating the Synthesis Gap with Expert Taxonomies}
{arXiv preprint, 2026}
{M. Zhang*\textsuperscript{\dag}, J. Zhuang*, W. Jing*, \textbf{K. Tan}*, Z. Kong, J. Deng, Y. Shen, et al.}
{\href{https://arxiv.org/abs/2601.12369}{Paper}}
{TaxoBench; deep research agents; expert taxonomy reconstruction; retrieval and organization metrics.}

\section*{Professional Experience}

\entry
{1Token Inc.}
{Shanghai, China}
{Growth Lead, Data \& Strategy}
{2022.07--2025.06}
\begin{itemize}
    \item Built global institutional databases and supported lead pipeline analysis, funding network mapping, and market research for data-driven growth strategy.
    \item Designed product-led-growth trials and improved online acquisition through growth analytics, SEO, website optimization, RPA, and NLP-based business attribute recognition.
\end{itemize}
\vspace{2pt}

\shortentry
{Earlier Research and Strategy Internships}
{2020--2022}
{1Token Growth Intern; Airwallex Operations Strategy Intern; MioTech Research Analyst Intern and China Concept Stock ESG Data Analyst Intern}

\section*{Education}

\entry
{The University of Tokyo}
{Tokyo, Japan}
{M.Eng., Technology Management for Innovation}
{2026.04--Present}

\entry
{Georgia Institute of Technology}
{Remote}
{Online M.S. in Computer Science, withdrawn; GPA: 90/100, 4.0/4.0}
{2024--2025}

\entry
{Fudan University}
{Shanghai, China}
{B.S., Mathematical Economics; GPA: 84/100, 3.15/4.0}
{2018.09--2022.06}

\shortentry
{Chengdu Foreign Languages School}
{2012.09--2018.06}
{Secondary Education; graduated with first place.}

\section*{Skills \& Activities}
\skillline{Programming / Markup}{Python; C; Java; HTML; CSS; JavaScript; Stata; R; MATLAB; MySQL; \LaTeX}
\skillline{Languages}{Chinese, native; English, fluent, TOEFL 108; Japanese / German / Russian, elementary}
\skillline{Activities}{Volunteer of Anti-2019-nCoV: collected hospital and victim data in Wuhan, searched for medical supplies, and translated WHO documents.}

\end{document}
